Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-10 draft/accordionComplexSurfaces.tex
infinite words

\begin{notation}
If~$c$ is an oriented cycle in~$Q$ such that~$c$ and~$c^2$ do not belong to the ideal of relations~$I$, we write:
\begin{itemize}
 \item $^\infty c$ for the infinite word:~$\cdots c c c$;
 \item $c^\infty$ for the word:~$c c c\cdots$;
 \item $^{-\infty} c$ for the infinite word:~$\cdots c^{-1} c^{-1} c^{-1}$;
 \item $c^{-\infty}$ for the word:~$c^{-1} c^{-1} c^{-1}\cdots$ and
 \item $^\infty c^\infty$ for the word:~$^\infty c c^\infty$.
\end{itemize}
\end{notation}

We note that~$(c^\infty)^{-1} =\,^{-\infty}c$ and similarly~$(^\infty c)^{-1} = c^{-\infty}$.

\begin{definition}
An \defn{eventually cyclic string} for~$\bar Q$ is a word~$\rho$ of the form~$^{\pm\infty}c_1\sigma c_2^{\pm\infty}$, where $c_1,c_2$ are oriented cycles in~$\bar Q$ (possibly of length zero), $c_1, c_1^2, c_2, c_2^2\notin I$, and~$\sigma$ is a finite string.
In case~$\rho=\,^{\pm\infty}c_1\sigma c_2^{\infty}$, it is called \defn{eventually direct}, and \defn{eventually inverse} if~$\rho=\,^{\pm\infty}c_1\sigma c_2^{-\infty}$.
\end{definition}

\begin{remark}
 The terminology in the previous definition is borrowed from~\ref{Crawley-Boevey}.
 Note however that our choice of convention differs from \emph{loc. cit.}, resulting in exchanging ``inverse'' and ``direct''.
\end{remark}

>>>>

\begin{notation}
If~$c$ is an oriented cycle in~$Q$ such that~$c$ and~$c^2$ do not belong to the ideal of relations~$I$, we write:
\begin{itemize}
 \item ${}^\infty c$ for the infinite word~$\cdots c c c$,
 \item $c^\infty$ for the infinite word~$c c c\cdots$,
% \item $^{-\infty} c$ for the infinite word~$\cdots c^{-1} c^{-1} c^{-1}$,
% \item $c^{-\infty}$ for the infinite word~$c^{-1} c^{-1} c^{-1}\cdots$, and
 \item $^\infty c^\infty$ for the bi-infinite word~$^\infty c c^\infty$.
\end{itemize}
We also define~${}^{-\infty}c \eqdef (c^\infty)^{-1}$ and similarly~$c^{-\infty} \eqdef (^\infty c)^{-1}$.
\end{notation}

\begin{definition}
An \defn{eventually cyclic string} for~$\bar Q$ is a word~$\rho$ of the form~$^{\pm\infty}c_1\sigma c_2^{\pm\infty}$, where $c_1,c_2$ are oriented cycles in~$\bar Q$ (possibly of length zero), $c_1, c_1^2, c_2, c_2^2\notin I$, and~$\sigma$ is a finite string.
\vincent{We also want $c_1\sigma \notin I$ or $c_1^{-1} \notin I$ depending on what we have...}
In case~$\rho=\,^{\pm\infty}c_1\sigma c_2^{\infty}$, it is called \defn{eventually direct}, and \defn{eventually inverse} if~$\rho=\,^{\pm\infty}c_1\sigma c_2^{-\infty}$.
\end{definition}

\begin{remark}
 The terminology in the previous definition is borrowed from~\cite{Crawley-Boevey}.
 Note however that our choice of convention differs from \emph{loc. cit.}, resulting in exchanging ``inverse'' and ``direct''.
\end{remark}
